When are Fuzzy Extractors Possible?

### 2014-10-01 info-bounds/FuzzyExtPossibility.tex
working to reorganize introduction

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
%The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.  
Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

\begin{abstract}
We characterize when deriving a stable key from a noisy source is possible.  We use the notation of fuzzy extractors introduced by Dodis et al. (Eurocrypt 2004).  The goal is to produce a strong $key$ from a $w$ drawn from a \emph{strong} distribution $W$ and to produce the same when given a nearby $w'$.  A fuzzy extractor is split into two algorithms $\gen$ which produces $key$ along with some helper information $p$ and $\rep$ which takes $w'$ and $p$ to reproduce $key$.  The key must remain strong in the presence of $p$.  The goal is to produce the correct key whenever $\dis(w, w')\le t$.
\anote{there is a big gap between theory and the needs of practice}

We identify a key quantity of a distribution called \emph{fuzzy min-entropy}.  Fuzzy min-entropy measures the maximum probability mass of a distribution that lies within a ball of radius $t$ in the metric space.  Ideally, key derivation should be possible whenever a distribution has fuzzy min-entropy.  In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

Current techniques for constructing fuzzy extractors lie far from this necessary condition.  We investigate whether this is inherent for both fuzzy extractors and secure sketches~(a one round information-reconciliation component).  Our constructions and impossibility results are information-theoretic.

We consider two types of fuzzy extractors and secure sketches.  The first we call \emph{distribution-aware}, the algorithms know the precise distribution they are trying to correct.  The second is \emph{distribution-oblivious} where $(\gen, \rep)$ must work for a family of distributions.

\textbf{Distribution-Aware} Whenever the fuzzy min-entropy is super-logarithmic, there exists a distribution-aware secure sketch and fuzzy extractor with super-logarithmic output entropy.  That is, fuzzy min-entropy is both a necessary and \emph{sufficient} condition for security in this setting.

\textbf{Distribution-Oblivious} The distribution-oblivious situation is more complicated.  Indeed, there is a significant difference between secure sketches and fuzzy extractors.  We show that there exist families of distributions where each distribution has fuzzy min-entropy such that any secure sketch is insecure.  However, it is possible to build a fuzzy extractor for these same family of distributions.
\bnote{come back to this.}
\end{abstract}

\section{Introduction}
\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}
\anote{should our results be seen as justifying the distribution specific approach?}
\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
Usually, authentication requires some high quality secret.  Traditionally, this secret is assumed to have high min-entropy.  However, many sources with sufficient entropy for authentication present an additional problem: noise.  That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.  To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings.

This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy}.  They identify two fundamental tasks in noisy key derivation.  The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.

A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.  Consider a particular high entropy distribution $W$.  Our goal is to derive stable keys from $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  
A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes the initial reading $w$ and produces $key$ along with a public helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.  The $key$ should hold even if an adversary has observed $p$~(the problem is trivial if $p$ is private).  The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.

Traditionally, fuzzy extractors are constructed by using a separate information-reconciliation component, known as a secure sketch, that maps $w'$ back to $w$ and a privacy-amplification component, a strong randomness extractor~\cite{nisan1993randomness}, that maps $w$ to a random key.  A secure sketch consists of a pair of algorithms $\sketch$ takes $w$ and produces a public value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.  The security losses incurred in information-reconciliation~(performed in secure sketches and fuzzy extractors) are larger than losses in privacy amplification.\bnote{should say something here about our understanding of privacy amplification and that extractors are necessary and sufficient} In the following discussion we describe limitations on fuzzy extractors.  This discussion applies to secure sketches as well. \bnote{should say you don't have to build secure sketches}

Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.  Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.  Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed and the remainder of the distribution is unknown 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.  Usually fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.

@@

Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
In the one-message setting, we are far from this ideal.

Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.  This loss is usually linear in the input length of the string.  While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.  As an example, many examples that arise in practice there are more error patterns than starting entropy.  Traditional fuzzy extractors provide no guarantee for sources of this type.  The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.  This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}

\paragraph{The price of distributional uncertainty}
As described above, fuzzy extractors are usually built for a family of distributions $\mathcal{W}$.  This strengthens the security guarantees: security holds as long as $W\in\mathcal{W}$.  In this work, we show that this uncertainty comes at a significant cost.  We consider two settings, first where the algorithms $\gen, \rep$ know the entire probability mass function of the distribution $W$.  We call this setting \emph{distribution aware}.\bnote{prior works on this setting}  The more traditional setting where security holds for a family of distributions $\mathcal{W}$ we call \emph{distribution-oblivious}.

In this work, we ask if super-logarithmic fuzzy min-entropy is sufficient for key derivation in both settings.  A distribution-oblivious fuzzy extractor for a family $\mathcal{W}$ is also a distribution-aware fuzzy extractor for all distributions in $\mathcal{W}$.   We ask the question for secure sketches and fuzzy extractors.

@@

\paragraph{Our Contribution} We first consider the \emph{distribution-aware} setting.  We show for a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).  Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.  In this work, we consider this minimal goal of a super-logarithmic length key.  If we require a longer output length this increases the requirement on fuzzy min-entropy.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

Our constructions are primarily feasibility results and do not run in polynomial time.  In the distribution-aware setting this seems necessary as most distributions have exponential description size.  The power of the distribution-aware setting is that the algorithms can access this description.  It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.

We then show the situation is worse in the distribution-oblivious setting.  We show that distributional uncertainty is a real drawback to providing security.  We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family is insecure~(\thref{thm:imposs sketch}).  Using a result of Fuller et al.~\cite{fuller2013computational}, this negative result extends to versions of secure sketches ensure $w$ has  pseudoentropy~(\corref{cor:extension to fuzz ext}).  Under very strong assumptions, computational secure sketches that provide unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.  Unpredictability is weaker than pseudoentropy and converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.  This negative result is quite strong, it allows the secure sketch to be wrong a $1/4$ of the time and requires the secure sketch to correct a sub constant fraction of errors.

\bnote{add a paragraph here about the negative result for fuzzy extractors}
\bnote{add a paragraph talking about the computational setting}
%The situation is significantly more complicated for distribution-oblivious algorithms.  Indeed, we show a natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.  However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.

\paragraph{Our approach} \bnote{say something about our methods.  leveled hashing, distributional uncertainty?}
\begin{table}
\begin{center}
\begin{tabular}{c | c | c }
& Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})
%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  All results are information-theoretic.}
\label{tab:main results}
\end{table}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  Finally, in \secref{sec:dist oblivious} we provide negative results for the distribution-oblivious setting.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We will also use an average case version of this notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
\begin{definition}[Conditional Hartley Entropy]
\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$. \bnote{there is nothing computational here right now}

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  For the remainder of this work we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.

>>>>

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.  
Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. To help eliminate noise, they produce a non secret helper string. This helper value allows the key to be regenerated from a nearby point.  Known constructions of fuzzy extractors do not provide security for most noisy distributions that occur in practice.

The nonsecret helper string allows an adversary to learn the generated key if they can guess a point close to the original reading.  A necessary condition to derive keys from a distribution is that no adversary can guess nearby points.  We call this condition \emph{fuzzy min-entropy}.  In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.  In this work, we ask whether fuzzy min-entropy is a sufficient condition for security in the fuzzy extractor setting.

A key impediment to providing security is distributional uncertainty.  We consider two settings, first where the fuzzy extractor knows the precise distribution and second the fuzzy extractor knows the distribution comes from some family.  We show that fuzzy min-entropy is a sufficient condition in the first setting and insufficient in the second setting.  That is, there is families of distributions with fuzzy min-entropy that no fuzzy extractor can derive keys from.  Our results are information-theoretic.

\bnote{keep editing}
\end{abstract}

\section{Introduction}
\anote{should our results be seen as justifying the distribution specific approach?}
\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
Usually, authentication requires some high quality secret.  Traditionally, this secret is assumed to have high min-entropy.  However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.  To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings. \lnote{Why limit to authentication}

 This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy} \lnote{BBR application was not, in fact, authentication}. \lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks in noisy key derivation.  The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.

A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  
A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.  The $key$ should be uniform even if an adversary has observed $p$.  The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.  For any security the initial readings must come from a high min-entropy distribution $W$.

\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.  Fix some distribution $W$.  The adversary has access to the reproduce function and attempts to learn the key by inputting a point.  Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.  For security, this must occur with negligible probability.  That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.  Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.  We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.  A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).  
We ask:  \emph{is fuzzy min-entropy sufficient for key derivation from noisy sources}?

We have evidence for the sufficiency of fuzzy min-entropy. In the interactive setting, fuzzy min-entropy is sufficient for both tasks under mild computational assumptions.  In the non-interactive setting, semantically secure multi-linear maps allow for strong key derivation.  We provide evidence it is possible under strong assumptions on the knowledge of $W$.  Thus, one might hope that  information-theoretic fuzzy extraction is possible for all distributions with fuzzy min-entropy.

\paragraph{Main result}
Our main result is negative~(\thref{thm:imposs sketch}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.   Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.  We show a family of distributions $\mathcal{W}$ such that no instantiation can be secure for all elements of $\mathcal{W}$.  Each possibility for the distribution $W$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).

\paragraph{The cost of distributional uncertainty}
Fuzzy extractors are designed with limited knowledge of the target distribution.  Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.  Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.

Our negative results show that when the distribution $W$ is sufficiently unknown, fuzzy extractors are impossible.  To illustrate that distributional uncertainty is the real problem, we define a restricted form of fuzzy extractor that is allowed to know the exact distribution $W$.  We call this a \emph{distribution-aware} fuzzy extractor.  In this setting, fuzzy min-entropy is a sufficient condition for key derivation~(\corref{cor:extension to fuzz ext}).

\paragraph{Information-reconciliation in isolation}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.

A secure sketch performs non-interactive information-reconciliation.  We show comparable results for secure sketches.  That is, there is a family of distributions for which no secure sketch in possible.  Furthermore, secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}).
\paragraph{Related Settings}
We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  We first consider the interactive setting.  
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is \bnote{what?}

\subsection{Old organization}

\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}

Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.  
Known constructions of fuzzy extractors and secure sketches incur significant losses.  In particular, for most practical noisy sources, there are no known secure sketches or fuzzy extractors.  In this work, we ask whether this is inherent.  We identify a key problem: uncertainty in the distribution of $W$.

@@

\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}

Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
In the one-message setting, we are far from this ideal. \lnote{Why frame it this way, effectively introducing a new scenario, when we could appeal to the first paragraphs of the intro and simply say ``consider, for a moment, removing the requirement that these tasks are performed with a single message''? Also a paper to cite: ``Secure computation w/o authentication'' by some superset of Canetti and Rabin; the reason we should cite this one rather than general MPC is that we don't want to assume authenticated channels here to start with}

\lnote{I don't think you want to talk about traditional constructions here yet. I think what you want to say, in light of the previous computational paragraph, is ``what about information-theoretic: is the necessary condition also sufficient''?}

Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.  This loss is usually linear in the input length of the string.  While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.  As an example, many examples that arise in practice there are more error patterns than starting entropy.  Traditional fuzzy extractors provide no guarantee for sources of this type.  The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.  This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}  To help answer this question, we identify a key problem: uncertainty in the distribution of $W$.

\paragraph{The price of distributional uncertainty}

\lnote{I think this should be ``Our Contributions'' and go in the following order. Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient. On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works. We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly). We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}

The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)

Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.  Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.  Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.  Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.

In this work, we show that this uncertainty comes at a significant cost.  We consider two settings, first where the algorithms $\gen, \rep$ know the probability mass function of the distribution $W$.  We call this setting \emph{distribution aware}.  Second, we consider the traditional setting where security holds for a family of distributions $\mathcal{W}$.  To distinguish it from the prior setting, we call it the \emph{distribution-oblivious} setting.
\anote{need to mention early work on trying to do distribution specific. For example, Juels and Wattenberg, Tuyls et al.}

In this work, we ask if super-logarithmic fuzzy min-entropy is sufficient for key derivation in both settings.  A distribution-oblivious fuzzy extractor for a family $\mathcal{W}$ is also a distribution-aware fuzzy extractor for all distributions in $\mathcal{W}$.   We ask the question for secure sketches and fuzzy extractors.  Our results are information-theoretic, we consider the implications of computational security after discussing our results.

\begin{table}
\begin{center}
\begin{tabular}{c | c | c }
& Distribution-Oblivious & Distribution-Aware\\
\hline
Secure Sketch & No~(\thref{thm:imposs sketch}) & Yes~(\thref{cons:leveling})\\
\hline
Fuzzy Extractor & No~(\thref{thm:imposs fuzz ext}) & Yes~(\corref{cor:extension to fuzz ext})
%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.  \lnote{I think this framing gives positive results too much attention. As we discussed on Monday, positive results here aren't what we want to emphasize}
We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).  Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.  In this work, we assume the goal is to produce a super-logarithmic length key.  In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

Our constructions are feasibility results and do not run in polynomial time.  In the distribution-aware setting this seems necessary as most distributions have exponential description size.  The power of the distribution-aware setting is that the algorithms can access this description.  It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.

\paragraph{Negative Results}
The situation is very different in the distribution-oblivious setting.  We show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family the remaining entropy is at most $1$~(\thref{thm:imposs sketch}).  This result only requires the secure sketch to correct a constant number of errors and to be correct $75\%$ of the time.

We then show a similar result to fuzzy extractors.  We show a similar family of distributions where no fuzzy extractor can extract even a single key bit~(\thref{thm:imposs fuzz ext}).  \thref{thm:imposs fuzz ext} has weaker parameters than \thref{thm:imposs sketch}.  (Ruling out a fuzzy extractor rules out a secure sketch with similar parameters so we expect the impossibility to have weaker parameters.)  Specifically, for a string of length $n$ the error tolerance required for the result is $t=\omega(n^{1/2}\log n)$.  Furthermore, the result only applies for fuzzy extractors with perfect correctness.  Many but not all fuzzy extractors have perfect correctness.

Both of negative results use families of distributions that are well-spread: all points of the distribution lie far apart.  Intuitively, this should be the easiest type of family to perform information-reconciliation.  In the distribution-aware setting, information-reconciliation requires no information.

\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.  Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.  Semantically secure multi-linear encodings are a very strong assumption.  Furthermore, the output is unpredictability~(not pseudoentropic).  Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.

Computational fuzzy extractors offer more hope for avoiding the impossibility result.  Computational fuzzy extractors for all distributions are implied by semantically secure multi-linear encodings~\cite{BitanskyCKP14}.  Furthermore, there are computational fuzzy extractors secure for the specific family of distributions used in the counter-example under weaker assumptions~\cite[Construction 5.3]{canetti2014key}.

\bnote{compare this with universal decoding?}

\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.  We call this type of distribution nearly flat.  The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.  Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.  We use universal hashing to disambiguate points.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions~(we call levels).  We then write down the level and apply the above construction considering only points in that level.  We call this construction leveled hashing: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

Our negative results are in the distribution-oblivious setting.  A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).  However, $\gen$ does not see the distribution $W$, only the sample $w$.  We construct a family of distributions $\mathcal{W}$ where even having seen $w$, the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  The value  $p$ partitions the metric space into possible and impossible $w$.  The partition is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  For both secure sketch and fuzzy extractors, we can show the set of possible $W|p$ is very small.  This is enough to contradict security for both secure sketches and fuzzy extractors.

\bnote{are these really affine lines?}
\bnote{I'm writing these, very rough draft}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$. % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$. 
 Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
